Analyzing the impact of social attributes on commit integration success

### 2017-03-14 Paper/MSRChallenge2017.tex
Submission version
changes to abstract

\begin{abstract}
As the software development community continues to make it easier for everyone
to contribute, the number of commits and pull requests keep increasing. However, this exciting growth
renders it more difficult to only accept quality contributions.
Recent research has found 
that both technical and social factors predict
the success of project contributions on GitHub.  
We take this question a step further, focusing on predicting continuous
integration build success based on technical and
social factors involved in a commit.
Specifically, we investigated if social factors (such as being a
core member of the development team, having a large number of followers,
or contributing a large number of commits) improve predictions of build
success.  We found that social factors cause a noticeable increase
in predictive power (12\%), core team members are more likely to pass the build
tests (10\%), and users with 1000 or more follower are more likely to
pass the build tests (10\%).
\end{abstract}

>>>>

\begin{abstract}
As the software development community makes it easier for everyone
to contribute to open source projects, the number of commits and pull requests 	
keep increasing. However, this exciting growth
renders it more difficult to only accept quality contributions.
Recent research has found 
that both technical and social factors predict
the success of project contributions on GitHub.  
We take this question a step further, focusing on predicting continuous
integration build success based on technical and
social factors involved in a commit.
Specifically, we investigated if social factors (such as being a
core member of the development team, having a large number of followers,
or contributing a large number of commits) improve predictions of build
success.  We found that social factors cause a noticeable increase
in predictive power (12\%), core team members are more likely to pass the build
tests (10\%), and users with 1000 or more followers are more likely to
pass the build tests (10\%).
\end{abstract}
